### 2018-07-31 manuscript.rmd
merged Nanomia sp in tree for analyses

#Prune tree to quant matrix species
nodatatipnames = consensus$tip.label[which(!(consensus$tip.label %in% sharedmatrix$Species))]
nodatatips = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames)]
prunedtree = drop.tip(consensus, nodatatips)
prunedtree$tip.label
plot(prunedtree)
ultram = chronos(prunedtree)
plot(ultram)

>>>>

#Prune tree to quant matrix species
nodatatipnames = consensus$tip.label[which(!(consensus$tip.label %in% sharedmatrix$Species))]
nodatatips = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames)]
prunedtree = drop.tip(consensus, nodatatips)
prunedtree$tip.label
plot(prunedtree)

#Switch nanomia_bijuga for sp
prunedtree$tip.label[which(prunedtree$tip.label == "Nanomia bijuga")] <- "Nanomia sp"

ultram = chronos(prunedtree)
plot(ultram)
